Granular measures of agricultural land-use influence lake nitrogen and phosphorus differently at macroscales

### 2020-07-23 manuscript/manuscript.Rmd
stash accepted/preprint version of ms

# Optional: line of arbitrary text with additional information.
# Could be used, for example, to mention the bibliographic info in a post-print.
# If not specified, defaults to "This version was compiled on \today"
#date_subtitle: Published in *Journal of Statistical Software*, 2018
date_subtitle: > 
  This is the accepted version of the following article: J. Stachelek et al., Ecological Applications. In Press, which has been published in final form at DOI:  [DOI](https://doi.org).  This article may be used for non-commercial purposes in accordance with Wiley Terms and Conditions for Use of Self-Archived Versions.

>>>>

# Optional: line of arbitrary text with additional information.
# Could be used, for example, to mention the bibliographic info in a post-print.
# If not specified, defaults to "This version was compiled on \today"
date_subtitle: > 
  This is the accepted version of the following article: J. Stachelek et al., Ecological Applications. 2020, which has been published in final form at DOI:  [10.1002/eap.2187](https://doi.org/10.1002/eap.2187).  This article may be used for non-commercial purposes in accordance with Wiley Terms and Conditions for Use of Self-Archived Versions.
